---
title: "Base reports"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Base reports}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


R provides functionally for checks in the tools package included by default on all R installations.

# Base functionality

```{r}
library("tools")
library("here") # To handle paths
```


The main function to check packages (besides `R CMD check`) is `check_packages_in_dir()`.

This function creates:

 1. Checks folders for the packages `pkgname.Rcheck`
 2. A `Library` with all the corresponding PACKAGES[.*] files
 3. A `timings.tab` file
 4. A `Outputs` folder with packages' checks and installation output.

The output on the R session is something along the lines of:

```{r}
#| eval: false
checks <- check_packages_in_dir(here("inst","source"))
```

The above code chunk is not run because it takes a while.
The output is:

```r
> checks
Check results for packages in dir
'C:\Code\Rprojects\riskreports\inst\source':
Package sources: 2, Reverse depends: 0
Use summary() for more information.
```

With the output of that function (class `check_packages_in_dir`) we can see the checks:

```r
> summary(checks)
Check results for packages in dir
'C:\Code\Rprojects\riskreports\inst\source':

Check status summary:
                  ERROR
  Source packages     2

Check results summary:
dplyr ... ERROR
* checking data for non-ASCII characters ... NOTE
* checking PDF version of manual ... WARNING
* checking PDF version of manual without index ... ERROR
riskmetric ... ERROR
* checking PDF version of manual ... WARNING
* checking PDF version of manual without index ... ERROR
```

But once the folder is created it can be used to create a data.frame via `check_packages_in_dir_details()`:

```{r}
details_source <- check_packages_in_dir_details(dir = here("inst", "source"))
details_manual <- check_packages_in_dir_details(dir = here("inst", "checks"))
details_manual_df <- as.data.frame(details_manual)
details_manual_df[, 1:4]
details_source_df <- as.data.frame(details_source)
details_source_df[, 1:4]
```

The fifth column contains details of the errors:

```{r}
details_source_df[, 5, drop = FALSE]
```

Also it might be relevant the timings:

```{r}
summarize_check_packages_in_dir_results(here("inst", "source"), full = TRUE)
summarize_check_packages_in_dir_timings(here("inst", "source"), full = TRUE)
# summarize_check_packages_in_dir_results("checks/", full = TRUE)
# summarize_check_packages_in_dir_timings("checks/") # No timings created
```

## What's missing


This doesn't inform about the platform or the settings used:

- Many of the checks are controlled via environmental variables (see`environ_report()`.
- Some other outputs can be affected by the `options()` set (see `options_report()`)
